---
title: "ddi: The Data Defect Index for Samples that May not be iid"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/kuriwaki/ddi.svg?branch=master)](https://travis-ci.com/kuriwaki/ddi)
[![CRAN status](https://www.r-pkg.org/badges/version/ddi)](https://CRAN.R-project.org/package=ddi)
<!-- badges: end -->

A simple set of functions to implement the Data Defect Index (d.d.i.), described in:

> Xiao-Li Meng. 2018. "Statistical Paradises and Paradoxes in big data (I): Law of Large Populations,  Big Data Paradox, and the 2016 US Presidential Election." _Annals of Applied  Statistics_ 12:2, 685–726. [doi:10.1214/18-AOAS1161SF](http://doi.org/10.1214/18-AOAS1161SF). 

([ungated version](https://statistics.fas.harvard.edu/files/statistics-2/files/statistical_paradises_and_paradoxes.pdf))


## Install

This package is currently on CRAN (0.1.0).

```{r, eval = FALSE}
install.packages("ddi")
```

Development versions can be downloaded via:

```{r, eval  = FALSE}
remotes::install_github("kuriwaki/ddi")
```


# Usage

With a dataframe with columns for a group's estimates and components of the formula, `ddc` computes the data defect correlation (&rho;).

An example dataset from the 2016 US Presidential Election is included (this also serves as the replication dataset for the AOAS article). The dataset compares official election results with estimates the Cooperative Congressional Election Study (CCES), the largest political survey in the US. The CCES micro-data is fully public and accessible at [its website](https://cces.gov.harvard.edu/). Here, we produce state-level estimates which are documented with `help(g2016)`.

```{r, message = FALSE}
library(ddi)
library(tidyverse)

data(g2016)
g2016
```

We can compute the data defect correlation just by plugging in some numbers. For example
```{r}
ddc(mu = 62984824/136639786, muhat = 12284/35829, N = 136639786, n = 35829)
```

and the d.d.i. is the square of that, about `r formatC(ddc(mu = 62984824/136639786, muhat = 12284/35829, N = 136639786, n = 35829)^2, digits = 7, format = "f")`. 

we got these numbers by 
```{r}
select(g2016, cces_pct_djt_vv, cces_n_vv, tot_votes, votes_djt) %>%
  summarize_all(sum)
```

where 

* `cces_totdjt_vv`: The count of Trump voters (among validated voters)
* `cces_n_vv`: The count of CCES validated voters (sample size)
* `votes_djt`: Total votes for Trump
* `tot_votes`: Total turnout
* `cces_pct_djt_vv`: Estimated vote share, `cces_totdjt_vv / cces_n_vv`
* `pct_djt_voters`: Estimated vote share, `votes_djt / tot_votes`


The function also takes vectors as inputs:
```{r}
with(g2016, ddc(mu = pct_djt_voters,
                muhat = cces_pct_djt_vv, 
                N = tot_votes, 
                n = cces_n_vv))
```

so can be implemented in a tibble as well:
```{r}
transmute(g2016, st,
          ddc = ddc(mu = pct_djt_voters, 
                    muhat = cces_pct_djt_vv, 
                    N = tot_votes,
                    n = cces_n_vv))
```

A negative &rho; means &rho; = Cor(_Respond_, 1(_Trump Supporter_)) < 0, i.e. Trump supporters were less likely to respond. 

