---
title: "d.d.i. (Data Defect Index) for non i.i.d. Samples"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A simple set of functions to implements Meng's Data Defect Index (d.d.i.).  

> Xiao-Li Meng. 2018. "Statistical paradises and paradoxes in big data (I): Law of large populations,  big data paradox, and the 2016 US presidential election." Annals of Applied  Statistics 12:2, 685–726. https://doi.org/10.1214/18-AOAS1161SF. 

([ungated version](https://statistics.fas.harvard.edu/files/statistics-2/files/statistical_paradises_and_paradoxes.pdf))


## Install

```{r, eval = FALSE}
# install.packages("devtools")
remotes::install_github("kuriwaki/ddi")
```



# Usage

With a dataframe with columns for a group's estimates and components of the formula, `ddc` computes the data defect correlation ($\rho$).

An example with the 2016 Election, which looks like

```{r, message = FALSE}
library(ddi)
library(tidyverse)

data(g2016)
g2016
```

Specify the column names for each component:
```{r}
ddcs <- ddc(g2016, 
            N = "tot_votes",
            n = "cces_n_vv",
            mu = "pct_djt_voters", 
            muhat = "cces_pct_djt_vv")
```

This returns:

```{r}
library(tibble)
print(tibble(st = g2016$st, ddc = ddcs), n = 51)
```


A negative $\rho$ means  $\rho = \text{Cor}(\textit{Respond}, \textit{Trump Supporter}) < 0$, i.e. Trump supporters were less likely to respond. 

